---
title: "My web page with Plotly"
author: "Koray KIRKAR"
date: "12/28/2020"
always_allow_html: true
output:
  ioslides_presentation: default
---

## Introduction

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

## Review criteria

The rubric contains the following two questions:

- Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
- Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## Visualization Code 1

Through this code we try to plot the closing prices of major European stock indices in the years of 1991 to 1998.

```{r echo=TRUE, eval=FALSE, message=FALSE, warning=FALSE}
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(dplyr))
data("EuStockMarkets")
stocks <- as.data.frame(EuStockMarkets) %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4))
plot_ly(stocks, x = ~time, y = ~price, color = ~index, mode = "lines")
```

## Visualization Plot 1

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(dplyr))
data("EuStockMarkets")
stocks <- as.data.frame(EuStockMarkets) %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4))
plot_ly(stocks, x = ~time, y = ~price, color = ~index, mode = "lines")
```

## Visualization Code 2

Using the `mtcars` dataset we plot can attempt to understand the relationship
of various factors to gas mileage (`mpg`).

We plot weight (`wt`) vs. mileage (`mpg`) spatially along the x/y axes. We 
visualize the number of cylinders (`cyl`) as colors and the amount of
horsepower (`hp`) as the size of an individual point in the plot.

```{r echo=TRUE, eval=FALSE, message=FALSE, warning=FALSE}
suppressPackageStartupMessages(library(plotly))
plot_ly(data = mtcars, x = ~wt, y = ~mpg, 
        color = ~as.factor(cyl), size = ~hp,
        text = ~paste("Weight: ", wt, '<br>MPG:', mpg),
        type = "scatter", mode = "markers") %>%
        layout(title = "Car Data")
```

## Visualization Plot 2

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
suppressPackageStartupMessages(library(plotly))
plot_ly(data = mtcars, x = ~wt, y = ~mpg, 
        color = ~as.factor(cyl), size = ~hp,
        text = ~paste("Weight: ", wt, '<br>MPG:', mpg),
        type = "scatter", mode = "markers") %>%
        layout(title = "Car Data")
```

## Thanks

Check the GitHUb Repository for this project.

[GitHUb Repo - Click Here.](https://github.com/kkirkar/plotly/)